Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-22 WSSSPE3/report/wg_main_software_credit.tex
Software credit appendix in progress; added some relevant pubs
Former-commit-id: d4910da9ce59d01dbc76b0bd5c003886b00bda70
adding a crossref and removing a comment
Added label
Added SC landing pages

\subsection{Topic} \todo{change the title to your topic}

@@

@@

\subsubsection{Landing Page}
\todo{link to landing page}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Software Credit Working Group}
\label{sec:software-credit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Publishing Software Working Group (\S\ref{sec:publishing-software}): publishing a software paper offers one mechanism for receiving credit

@@

\subsubsection{Landing Page}

Since near-term efforts will be shifting to the FORCE11 Software Citation Working Group (SCWG), we direct interested readers to that group's existing landing page\footnote{FORCE11-SCWG landing page, \url{https://www.force11.org/group/software-citation-working-group}} and GitHub repository\footnote{FORCE11-SCWG GitHub page,  \url{https://github.com/force11/force11-scwg}}.
